### 2023-04-24 paper/treats_paper.tex
rename paper

\newcommand{\dads}{\texttt{dads} }

@@

%Running head
\begin{flushright}
Version dated: \today
\end{flushright}
\bigskip
\noindent RH: \dads package.

@@

\noindent{\Large \bf \dads: a modular \texttt{R} package for simulating diversity and traits data.} 
\bigskip

@@

        \item Here I present the \dads package, a modular \texttt{R} package for diversity and trait disparity simulations.
        This package is based on a standard birth death algorithm that can be easily tuned to the user specific needs by designing their specific trait process, birth-death modifiers and events.
        It also provides a tidy interface through the \dads object, allowing users to easily run reproducible simulations.

        \item The \dads package also comes with an extend manual regularly updated following users' questions or suggestions.

@@

% The solution with dads
Therefore, we propose \dads a modular \texttt{R} package to simulate both diversity and disparity through time.

\section{Description}
% Very briefly how does it work
\dads is based on a core birth-death process implemented in the function \texttt{dads} that simulates diversity through time using the following steps:

@@

In \dads, these three or four steps are implemented as modular functions that the user can easily change using an internal class of objects called \texttt{``modifiers''} or \texttt{``traits''} (Fig. \ref{Fig:workflow}).
The simulation then outputs a tree (of class \texttt{``phylo''} and a associated table of traits - \texttt{``matrix''}) that can be visualised using the \texttt{plot.dads} function.

\begin{figure}[!htbp]
\centering
   \includegraphics[width=1\textwidth]{../inst/gitbook/dads_structure.pdf} 
\caption{\dads package workflow: @@@.}
\label{Fig:workflow}
\end{figure}
% \texttt{"events"} are an additional category of modular objects discussed later.

@@

\texttt{## Running a simulation with a speciation rate of 1, an extinction rate of 0.1 and stopping when it reaches 20 taxa}
\texttt{my_simulation <- dads(bd.params = list(speciation = 1, extinction = 0.1), stop.rule = list(max.taxa = 20))}

@@

These are included by default in a \texttt{dads} process but can be also set manually by creating a \texttt{``modifiers''} object with no options:

\texttt{## Generating the default modifiers}
\texttt{my_modifiers <- make.modifiers()}
\texttt{## Running a simulation with a speciation rate of 1, an extinction rate of 0.1 and stopping when it reaches 20 taxa with the default modifiers}
\texttt{my_simulation <- dads(bd.params = list(speciation = 1, extinction = 0), stop.rule = list(max.taxa = 20), modifiers = my_modifiers)}

@@

\subsection{\dads compared to other packages}

@@

\section{Conclusion}
The \dads is modular and nice to use.

\section{Package location}
The \dads package is available on the CRAN at \url{https://cran.r-project.org/web/packages/dads/index.html} or on GitHub at \url{https://github.com/TGuillerme/dads} with more associated information.
All the versions of the package are archived on ZENODO with associated DOI \url{https://zenodo.org/@@@}.

>>>>

\newcommand{\treats}{\texttt{treats} }

@@

%Running head
\begin{flushright}
Version dated: \today
\end{flushright}
\bigskip
\noindent RH: \treats package.

@@

\noindent{\Large \bf \treats: a modular \texttt{R} package for simulating diversity and traits data.} 
\bigskip

@@

        \item Here I present the \treats package, a modular \texttt{R} package for diversity and trait disparity simulations.
        This package is based on a standard birth death algorithm that can be easily tuned to the user specific needs by designing their specific trait process, birth-death modifiers and events.
        It also provides a tidy interface through the \treats object, allowing users to easily run reproducible simulations.

        \item The \treats package also comes with an extend manual regularly updated following users' questions or suggestions.

@@

% The solution with treats
Therefore, we propose \treats a modular \texttt{R} package to simulate both diversity and disparity through time.

\section{Description}
% Very briefly how does it work
\treats is based on a core birth-death process implemented in the function \texttt{treats} that simulates diversity through time using the following steps:

@@

In \treats, these three or four steps are implemented as modular functions that the user can easily change using an internal class of objects called \texttt{``modifiers''} or \texttt{``traits''} (Fig. \ref{Fig:workflow}).
The simulation then outputs a tree (of class \texttt{``phylo''} and a associated table of traits - \texttt{``matrix''}) that can be visualised using the \texttt{plot.treats} function.

\begin{figure}[!htbp]
\centering
   \includegraphics[width=1\textwidth]{../inst/gitbook/treats_structure.pdf} 
\caption{\treats package workflow: @@@.}
\label{Fig:workflow}
\end{figure}
% \texttt{"events"} are an additional category of modular objects discussed later.

@@

\texttt{## Running a simulation with a speciation rate of 1, an extinction rate of 0.1 and stopping when it reaches 20 taxa}
\texttt{my_simulation <- treats(bd.params = list(speciation = 1, extinction = 0.1), stop.rule = list(max.taxa = 20))}

@@

These are included by default in a \texttt{treats} process but can be also set manually by creating a \texttt{``modifiers''} object with no options:

\texttt{## Generating the default modifiers}
\texttt{my_modifiers <- make.modifiers()}
\texttt{## Running a simulation with a speciation rate of 1, an extinction rate of 0.1 and stopping when it reaches 20 taxa with the default modifiers}
\texttt{my_simulation <- treats(bd.params = list(speciation = 1, extinction = 0), stop.rule = list(max.taxa = 20), modifiers = my_modifiers)}

@@

\subsection{\treats compared to other packages}

@@

\section{Conclusion}
The \treats is modular and nice to use.

\section{Package location}
The \treats package is available on the CRAN at \url{https://cran.r-project.org/web/packages/treats/index.html} or on GitHub at \url{https://github.com/TGuillerme/treats} with more associated information.
All the versions of the package are archived on ZENODO with associated DOI \url{https://zenodo.org/@@@}.
